A Realistic Guide to Making Data Available Alongside Code to Improve Reproducibility

### 2019-06-13 paper.Rmd
Removed duplicate headings
added code images and suppress library messages

```{r setup, echo = FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      out.width = "100%")

library(kableExtra)
```

@@

```{r fig-effort-understanding, fig.cap = "There is a big difference in the effort to prepare data, and how easy it is to understand - look at the difference between most datasets, and something like a Randomized Control Trial (RCT)."}
library(ggplot2)

@@

library(tibble)

@@

library(ggrepel)

@@

## Higher potential impact means more time**

@@

```
proj-name/
         |
         | - README.md
         | - Codebook.csv
         | - LICENSE.md
         | - metadata.json
         | - raw-data/
                     | - raw-data.csv
                     | - 01-read-tidy-raw-data.csv
         | - data/
                 | - final-data.csv
```

_Figure XX. Example directory layout and structure for a data repository._

@@

The data dictionary provides _human readable_ information on the data. To ensure data types are preserved - dates are dates, names are characters, and so on - there needs to be some form of _machine readable_ metadata. An excellent standard for metadata is Table Schema written by frictionless data [@fritionless-table-schema]. Say for a dataset called "demographics" with three variables (Table \@ref(tab:table-machine-readable))

@@

```
{
  "name": "demographics",
  # here we list the data files in this dataset
  "resources": [
    {
      "path": "demographics.csv",
      "schema": {
        "fields": [
          {
            "name": "age",
            "type": "integer"
          },
          {
            "name": "height",
            "type": "number"
          },
          {
            "name": "nationality",
            "type": "string"
          }
        ]
      }
    }
  ]
}
```

_Figure XX Example snippet of some Table Schema data for a dataset with three variables. This provides a description of each field, and the type of field, and it's description._

@@

sdss_image_path <- here::here("figures", "sdss-spectra-example-plate-1678.png")
library(magick)
library(ggplot2)
library(cowplot)

@@

```{r spectra-tab, echo = FALSE}
library(kableExtra)
head(spectra) %>%
  knitr::kable(caption = "Example spectra data from SDSS, showing values for Wavelength, Flux, BestFit, and SkyFlux.",
               booktabs = TRUE) %>%
  kable_styling(latex_options = c("striped",
                                  "hold_position"))

@@

# Ten simple rules for publishing data {#10-rules}

>>>>

```{r setup, echo = FALSE}

knitr::opts_chunk$set(echo = FALSE,
                      out.width = "100%")

suppressMessages(library(ggrepel))
suppressMessages(library(tibble))
suppressMessages(library(kableExtra))
suppressMessages(library(magick))
suppressMessages(library(ggplot2))
suppressMessages(library(cowplot))
```

@@

```{r fig-effort-understanding, fig.cap = "There is a big difference in the effort to prepare data, and how easy it is to understand - look at the difference between most datasets, and something like a Randomized Control Trial (RCT)."}

@@

@@

@@

## Higher potential impact means more time

@@

One basic suggested directory layout is given below in Figure \@ref(fig:code-directory).

```{r code-directory, out.width = "75%", fig.align = "center", fig.cap = "Example directory layout and structure for a data repository."}
knitr::include_graphics(here::here("figures",
                                   "directory-structure.png"))
```

@@

The data dictionary provides _human readable_ information on the data. To ensure data types are preserved - dates are dates, names are characters, and so on - there needs to be some form of _machine readable_ metadata. An excellent standard for metadata is Table Schema written by frictionless data [@fritionless-table-schema]. Say for a dataset called "demographics" with three variables (Table \@ref(tab:table-machine-readable)) and JSON equivalent in Figure \@ref(fig:json-code).

@@

```{r json-code, fig.align = "center", out.width = "75%", fig.cap = "Example snippet of some Table Schema data for a dataset with three variables. This provides a description of each field, and the type of field, and it's description."}
knitr::include_graphics(here::here("figures",
                                   "json-code.png"))
```

@@

sdss_image_path <- here::here("figures", "sdss-spectra-example-plate-1678.png")

@@

```{r spectra-tab, echo = FALSE}

head(spectra) %>%
  knitr::kable(caption = "Example spectra data from SDSS, showing values for Wavelength, Flux, BestFit, and SkyFlux.",
               booktabs = TRUE) %>%
  kable_styling(latex_options = c("striped",
                                  "hold_position"))

@@

# Ten simple rules for publishing data {#ten-rules}
